Report

### 2021-05-13 Rmd/report.Rmd
Simplify report code.

@@

```{r gaze_trial_21, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_trial %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	mutate(age_group = paste0(age_group, " months")) %>% 
	filter(valid_participant, valid_trial, age_group == "21 months") %>% 
	group_by(participant, lp, trial_type, age_group, location) %>% 
	summarise(prop_target = mean(prop_target),
			  prop_distractor = mean(prop_distractor),
			  .groups = "drop") %>% 
	pivot_longer(c("prop_target", "prop_distractor"), names_to = "aoi", values_to = "prop") %>% 
	mutate(aoi = str_to_sentence(str_remove(aoi, "prop_"))) %>% 
	drop_na() %>% 
	ggplot(aes(aoi, prop, colour = aoi, fill = aoi)) +
	facet_grid(trial_type~lp) +
	geom_violin() +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_line(aes(group = participant), colour = "grey", alpha = 0.5) +
	#stat_slab(position = position_nudge(x = 0.25)) +
	geom_boxplot(aes(group = interaction(aoi, trial_type)), width = 0.1, colour = "black", fill = "white", outlier.colour = NA) +
	#geom_point(size = 2, shape = 1, stroke = 1) +
	labs(x = "AOI", y = "Target looking / Total looking", colour = "AOI", fill = "AOI") + 
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme_bilingual() +
	theme(
		legend.position = "none",
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
	) +
	ggsave(here("Figures", "gaze_trial_21.png"))

@@

```{r gaze_trial_25, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_trial %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	mutate(age_group = paste0(age_group, " months")) %>% 
	filter(valid_participant, valid_trial, age_group == "25 months") %>% 
	group_by(participant, lp, trial_type, age_group, location) %>% 
	summarise(prop_target = mean(prop_target),
			  prop_distractor = mean(prop_distractor),
			  .groups = "drop") %>% 
	pivot_longer(c("prop_target", "prop_distractor"), names_to = "aoi", values_to = "prop") %>% 
	mutate(aoi = str_to_sentence(str_remove(aoi, "prop_"))) %>% 
	drop_na() %>% 
	ggplot(aes(aoi, prop, colour = aoi, fill = aoi)) +
	facet_grid(trial_type~lp) +
	geom_violin() +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_line(aes(group = participant), colour = "grey", alpha = 0.5) +
	#stat_slab(position = position_nudge(x = 0.25)) +
	geom_boxplot(aes(group = interaction(aoi, trial_type)), width = 0.1, colour = "black", fill = "white", outlier.colour = NA) +
	#geom_point(size = 2, shape = 1, stroke = 1) +
	labs(x = "AOI", y = "Target looking / Total looking", colour = "AOI", fill = "AOI") + 
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme_bilingual() +
	theme(
		legend.position = "none",
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
	) +
	ggsave(here("Figures", "gaze_trial_25.png"))
```

@@

```{r gaze_trial_30, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_trial %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	mutate(age_group = paste0(age_group, " months")) %>% 
	filter(valid_participant, valid_trial, age_group == "30 months") %>% 
	group_by(participant, lp, trial_type, age_group, location) %>% 
	summarise(prop_target = mean(prop_target),
			  prop_distractor = mean(prop_distractor),
			  .groups = "drop") %>% 
	pivot_longer(c("prop_target", "prop_distractor"), names_to = "aoi", values_to = "prop") %>% 
	mutate(aoi = str_to_sentence(str_remove(aoi, "prop_"))) %>% 
	drop_na() %>% 
	ggplot(aes(aoi, prop, colour = aoi, fill = aoi)) +
	facet_grid(trial_type~lp) +
	geom_violin() +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_line(aes(group = participant), colour = "grey", alpha = 0.5) +
	#stat_slab(position = position_nudge(x = 0.25)) +
	geom_boxplot(aes(group = interaction(aoi, trial_type)), width = 0.1, colour = "black", fill = "white", outlier.colour = NA) +
	#geom_point(size = 2, shape = 1, stroke = 1) +
	labs(x = "AOI", y = "Target looking / Total looking", colour = "AOI", fill = "AOI") + 
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme_bilingual() +
	theme(
		legend.position = "none",
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
	) +
	ggsave(here("Figures", "gaze_trial_30.png"))

@@

gaze_time_vocab_d <- gaze_time %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	left_join(select(participants, participant, age_group, vocab_size)) %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(time_bin, trial_type, lp, age_group,location, vocab_size) %>% 
	summarise(
		prop_target = mean(prop_target, na.rm = TRUE),
		prop_distractor = mean(prop_distractor, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	pivot_longer(c(prop_target, prop_distractor), names_to = "aoi", values_to = "prop") %>% 
	ungroup() %>% 
	mutate(
		se = sqrt((prop*(1-prop))/(n+4)),
		lower = prop-se,
		upper = prop+se,
		time_bin = time_bin*100,
		vocab_cat = ifelse(
			vocab_size < median(.$vocab_size, na.rm = TRUE),
			"Below the median",
			"Above the median"
		),
		age_group = paste0(age_group, " months"),
		aoi = str_to_sentence(str_remove(aoi, "prop_"))
	) %>% 
	drop_na()

@@

gaze_time_vocab_d %>% 
	filter(age_group == "21 months") %>% 
	ggplot(aes(
		x = time_bin, y = prop,
		colour = interaction(vocab_cat, aoi, sep = " - "),
		fill = interaction(vocab_cat, aoi, sep = " - "),
		shape = interaction(vocab_cat, aoi, sep = " - ")
	)
	) +
	facet_grid(lp~trial_type) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	#geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	#geom_point(alpha = 0.5) +
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Vocab-AOI",
		 fill = "Vocab-AOI", shape = "Vocab-AOI") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.position = "right",
		  panel.grid = element_line(colour = "grey", linetype = "dotted"))
```

@@

gaze_time_vocab_d %>% 
	filter(age_group == "25 months") %>% 
	ggplot(aes(
		x = time_bin, y = prop,
		colour = interaction(vocab_cat, aoi, sep = " - "),
		fill = interaction(vocab_cat, aoi, sep = " - "),
		shape = interaction(vocab_cat, aoi, sep = " - ")
	)
	) +
	facet_grid(lp~trial_type) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	#geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	#geom_point(alpha = 0.5) +
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Vocab-AOI",
		 fill = "Vocab-AOI", shape = "Vocab-AOI") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.position = "right",
		  panel.grid = element_line(colour = "grey", linetype = "dotted"))
```

@@

gaze_time_vocab_d %>% 
	filter(age_group == "30 months") %>% 
	ggplot(aes(
		x = time_bin, y = prop,
		colour = interaction(vocab_cat, aoi, sep = " - "),
		fill = interaction(vocab_cat, aoi, sep = " - "),
		shape = interaction(vocab_cat, aoi, sep = " - ")
	)
	) +
	facet_grid(lp~trial_type) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	#geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	#geom_point(alpha = 0.5) +
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Vocab-AOI",
		 fill = "Vocab-AOI", shape = "Vocab-AOI") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.position = "right",
		  panel.grid = element_line(colour = "grey", linetype = "dotted"))
```

@@

gaze_time_vocab_d %>% 
	filter(age_group == "21 months") %>% 
	ggplot(aes(
		x = time_bin, y = prop,
		colour = interaction(location, aoi, sep = "-"),
		fill = interaction(location, aoi, sep = "-"),
		shape = interaction(location, aoi, sep = "-")
	)) +
	facet_grid(lp~trial_type) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	#geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	#geom_point(alpha = 0.5) +
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "AOI", fill = "AOI", shape = "AOI") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.title = element_blank(),
		  legend.position = "right",
		  panel.grid = element_line(colour = "grey", linetype = "dotted"))
```

@@

gaze_time_vocab_d %>% 
	filter(age_group == "25 months") %>% 
	ggplot(aes(
		x = time_bin, y = prop,
		colour = interaction(location, aoi, sep = "-"),
		fill = interaction(location, aoi, sep = "-"),
		shape = interaction(location, aoi, sep = "-")
	)) +
	facet_grid(lp~trial_type) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	#geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	#geom_point(alpha = 0.5) +
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Location-AOI",
		 fill = "Location-AOI", shape = "Location-AOI") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.position = "right",
		  panel.grid = element_line(colour = "grey", linetype = "dotted"))

@@

gaze_time_vocab_d %>% 
	filter(age_group == "30 months") %>% 
	ggplot(aes(
		x = time_bin, y = prop,
		colour = interaction(location, aoi, sep = "-"),
		fill = interaction(location, aoi, sep = "-"),
		shape = interaction(location, aoi, sep = "-")
	)) +
	facet_grid(lp~trial_type) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	#geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	#geom_point(alpha = 0.5) +
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Location-AOI",
		 fill = "Location-AOI", shape = "Location-AOI") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.position = "right",
		  panel.grid = element_line(colour = "grey", linetype = "dotted"))

>>>>

```{r gaze_trial, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
gaze_trial_age <- gaze_trial %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	mutate(age_group = paste0(age_group, " months")) %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(participant, lp, trial_type, age_group, location) %>% 
	summarise(prop_target = mean(prop_target),
			  prop_distractor = mean(prop_distractor),
			  .groups = "drop") %>% 
	pivot_longer(c("prop_target", "prop_distractor"), names_to = "aoi", values_to = "prop") %>% 
	mutate(aoi = str_to_sentence(str_remove(aoi, "prop_"))) %>% 
	drop_na() %>% 
	split(f = .$age_group) %>% 
	set_names(c("21", "25", "30"))
```

@@

```{r gaze_trial_21, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

ggplot(gaze_trial_age[["21"]], aes(aoi, prop, colour = aoi, fill = aoi)) +
	facet_grid(lp~trial_type) +
	geom_violin() +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_line(aes(group = participant), colour = "grey", alpha = 0.5) +
	#stat_slab(position = position_nudge(x = 0.25)) +
	geom_boxplot(aes(group = interaction(aoi, trial_type)), width = 0.1, colour = "black", fill = "white", outlier.colour = NA) +
	#geom_point(size = 2, shape = 1, stroke = 1) +
	labs(x = "AOI", y = "Target looking / Total looking", colour = "AOI", fill = "AOI") + 
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme_bilingual() +
	theme(
		legend.position = "none",
		axis.title.x = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
	) +
	ggsave(here("Figures", "gaze_trial_21.png"))

@@

```{r gaze_trial_25, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplot(gaze_trial_age[["25"]], aes(aoi, prop, colour = aoi, fill = aoi)) +
	facet_grid(lp~trial_type) +
	geom_violin() +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_line(aes(group = participant), colour = "grey", alpha = 0.5) +
	#stat_slab(position = position_nudge(x = 0.25)) +
	geom_boxplot(aes(group = interaction(aoi, trial_type)), width = 0.1, colour = "black", fill = "white", outlier.colour = NA) +
	#geom_point(size = 2, shape = 1, stroke = 1) +
	labs(x = "AOI", y = "Target looking / Total looking", colour = "AOI", fill = "AOI") + 
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme_bilingual() +
	theme(
		legend.position = "none",
		axis.title.x = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
	) +
	ggsave(here("Figures", "gaze_trial_25.png"))
```

@@

```{r gaze_trial_30, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplot(gaze_trial_age[["30"]], aes(aoi, prop, colour = aoi, fill = aoi)) +
	facet_grid(lp~trial_type) +
	geom_violin() +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_line(aes(group = participant), colour = "grey", alpha = 0.5) +
	#stat_slab(position = position_nudge(x = 0.25)) +
	geom_boxplot(aes(group = interaction(aoi, trial_type)), width = 0.1, colour = "black", fill = "white", outlier.colour = NA) +
	#geom_point(size = 2, shape = 1, stroke = 1) +
	labs(x = "AOI", y = "Target looking / Total looking", colour = "AOI", fill = "AOI") + 
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme_bilingual() +
	theme(
		legend.position = "none",
		axis.title.x = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
	) +
	ggsave(here("Figures", "gaze_trial_30.png"))

@@

gaze_time_vocab_d <- gaze_time %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	left_join(select(participants, participant, age_group, vocab_size)) %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(time_bin, trial_type, lp, age_group,location, vocab_size) %>% 
	summarise(
		prop_target = mean(prop_target, na.rm = TRUE),
		prop_distractor = mean(prop_distractor, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	pivot_longer(c(prop_target, prop_distractor), names_to = "aoi", values_to = "prop") %>% 
	ungroup() %>% 
	mutate(
		se = sqrt((prop*(1-prop))/(n+4)),
		lower = prop-se,
		upper = prop+se,
		time_bin = time_bin*100,
		vocab_cat = ifelse(
			vocab_size < median(.$vocab_size, na.rm = TRUE),
			"Below the median",
			"Above the median"
		),
		age_group = paste0(age_group, " months"),
		aoi = str_to_sentence(str_remove(aoi, "prop_"))
	) %>% 
	drop_na() %>% 
	split(f = .$age_group) %>% 
	set_names(c("21", "25", "30"))

@@

ggplot(
	gaze_time_vocab_d[["21"]],
	aes(
		x = time_bin, y = prop,
		colour = interaction(vocab_cat, aoi, sep = " - "),
		fill = interaction(vocab_cat, aoi, sep = " - "),
		shape = interaction(vocab_cat, aoi, sep = " - ")
	)
) +
	facet_grid(lp~trial_type) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	#geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	#geom_point(alpha = 0.5) +
	labs(x = "Time (ms)", y = "Fixations", colour = "Vocabulary-AOI",
		 fill = "Vocabulary-AOI", shape = "Vocabulary-AOI") +
	guides(
		fill = guide_legend(ncol = 2),
		colour = guide_legend(ncol = 2),
		shape = guide_legend(ncol = 2)
	) +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.position = "top",
		  panel.grid = element_line(colour = "grey", linetype = "dotted"))
```

@@

ggplot(
	gaze_time_vocab_d[["25"]],
	aes(
		x = time_bin, y = prop,
		colour = interaction(vocab_cat, aoi, sep = " - "),
		fill = interaction(vocab_cat, aoi, sep = " - "),
		shape = interaction(vocab_cat, aoi, sep = " - ")
	)
) +
	facet_grid(lp~trial_type) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	#geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	#geom_point(alpha = 0.5) +
	labs(x = "Time (ms)", y = "Fixations", colour = "Vocabulary-AOI",
		 fill = "Vocabulary-AOI", shape = "Vocabulary-AOI") +
	guides(
		fill = guide_legend(ncol = 2),
		colour = guide_legend(ncol = 2),
		shape = guide_legend(ncol = 2)
	) +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.position = "top",
		  panel.grid = element_line(colour = "grey", linetype = "dotted"))
```

@@

ggplot(
	gaze_time_vocab_d[["21"]],
	aes(
		x = time_bin, y = prop,
		colour = interaction(vocab_cat, aoi, sep = " - "),
		fill = interaction(vocab_cat, aoi, sep = " - "),
		shape = interaction(vocab_cat, aoi, sep = " - ")
	)
) +
	facet_grid(lp~trial_type) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	#geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	#geom_point(alpha = 0.5) +
	labs(x = "Time (ms)", y = "Fixations", colour = "Vocabulary-AOI",
		 fill = "Vocabulary-AOI", shape = "Vocabulary-AOI") +
	guides(
		fill = guide_legend(ncol = 2),
		colour = guide_legend(ncol = 2),
		shape = guide_legend(ncol = 2)
	) +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.position = "top",
		  panel.grid = element_line(colour = "grey", linetype = "dotted"))
```

@@

ggplot(
	gaze_time_vocab_d[["21"]],
	aes(
		x = time_bin, y = prop,
		colour = interaction(location, aoi, sep = "-"),
		fill = interaction(location, aoi, sep = "-"),
		shape = interaction(location, aoi, sep = "-")
	)) +
	facet_grid(lp~trial_type) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	#geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	#geom_point(alpha = 0.5) +
	labs(x = "Time (ms)", y = "Fixations", colour = "AOI", fill = "AOI", shape = "AOI") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.title = element_blank(),
		  legend.position = "top",
		  panel.grid = element_line(colour = "grey", linetype = "dotted"))
```

@@

ggplot(
	gaze_time_vocab_d[["25"]],
	aes(
		x = time_bin, y = prop,
		colour = interaction(location, aoi, sep = "-"),
		fill = interaction(location, aoi, sep = "-"),
		shape = interaction(location, aoi, sep = "-")
	)) +
	facet_grid(lp~trial_type) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	#geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	#geom_point(alpha = 0.5) +
	labs(x = "Time (ms)", y = "Fixations", colour = "Location-AOI",
		 fill = "Location-AOI", shape = "Location-AOI") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.position = "top",
		  panel.grid = element_line(colour = "grey", linetype = "dotted"))

@@

ggplot(
	gaze_time_vocab_d[["30"]],
	aes(
		x = time_bin, y = prop,
		colour = interaction(location, aoi, sep = "-"),
		fill = interaction(location, aoi, sep = "-"),
		shape = interaction(location, aoi, sep = "-")
	)) +
	facet_grid(lp~trial_type) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	#geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	#geom_point(alpha = 0.5) +
	labs(x = "Time (ms)", y = "Fixations", colour = "Location-AOI",
		 fill = "Location-AOI", shape = "Location-AOI") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.position = "right",
		  panel.grid = element_line(colour = "grey", linetype = "dotted"))
